Parallel Monte Carlo Synthetic Acceleration Methods for Discrete Transport Problems

### 2013-09-09 doc/dissertation/presentation/defense.tex
updating date in defense talk

\date{\today} 
\title{Parallel Monte Carlo Synthetic Acceleration Methods for
  Discrete Transport Problems}
\begin{document}
\maketitle

@@

{\tiny  \begin{table}[h!]
    \begin{center}
      \begin{tabular}{cccccc}\hline\hline
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{$SP_N$ Order}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{} \\
        &   & \textbf{1} & \textbf{3} & \textbf{5} & \textbf{7}  \\
        & \textbf{0} & 0.0647 & 0.1275 & 0.1449 & 0.1514 \\
        & \textbf{1} & 0.0686 & 0.1338 & 0.1484 & 0.1547 \\
        $P_N$ Order & \textbf{3} & 0.0687 & 0.1399 & 0.1582 & 0.1625 \\
        & \textbf{5} & 0.0692 & 0.1399 & 0.1582 & 0.1657 \\
        & \textbf{7} & 0.0678 & 0.1393 & 0.1624 & 0.166 \\
        %%
        \hline\hline
      \end{tabular}
    \end{center}
    \caption{Spectral radius results for the block Jacobi
      preconditioned iteration matrix with 10 energy groups and full
      downscatter for sample problem.}
    \label{tab:group10dsbj}
  \end{table}
}

@@

      \begin{figure}[t!]
        \begin{center}
          \includegraphics[width=2.0in]{block_jacobi_res.pdf}
        \end{center}
      \end{figure}

@@

    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item Rapidly divergent results
        \medskip
      \item Light water moderator creates a lot of scattering and
        $\mathbf{\rho}(\mathbf{H}) \approx 1$
        \medskip
      \item Convergence not achieved with 50 histories per DOF and 90
        minutes compute time
      \end{itemize}
    \end{column}

@@

      \begin{itemize}
        {\small
        \item Comparison to Trilinos Aztec Krylov solvers with ILUT
          \medskip
        \item MCLS verified for the k-eigenvalue and neutron flux in
          all groups
          \medskip
        \item MCSA converged in fewer iterations than GMRES, more
          iterations than BiCGStab
          \medskip
        \item Explicit preconditioning strategy destroys sparsity and
          elevates CPU times (Ifpack ILUT)
          \medskip
        \item Spectral radius and memory limitations combine to
          prevent solutions at finer discretizations
        }
      \end{itemize}

>>>>

\date{September 9, 2013} 
\title{Parallel Monte Carlo Synthetic Acceleration Methods for
  Discrete Transport Problems}
\begin{document}
\maketitle

@@

{\tiny  \begin{table}[h!]
    \begin{center}
      \begin{tabular}{cccccc}\hline\hline
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{$SP_N$ Order}& 
        \multicolumn{1}{c}{}& 
        \multicolumn{1}{c}{} \\
        &   & \textbf{1} & \textbf{3} & \textbf{5} & \textbf{7}  \\
        & \textbf{0} & 0.0647 & 0.1275 & 0.1449 & 0.1514 \\
        & \textbf{1} & 0.0686 & 0.1338 & 0.1484 & 0.1547 \\
        $P_N$ Order & \textbf{3} & 0.0687 & 0.1399 & 0.1582 & 0.1625 \\
        & \textbf{5} & 0.0692 & 0.1399 & 0.1582 & 0.1657 \\
        & \textbf{7} & 0.0678 & 0.1393 & 0.1624 & 0.166 \\
        %%
        \hline\hline
      \end{tabular}
    \end{center}
    \caption{Spectral radius results for the block Jacobi
      preconditioned $SP_N$ iteration matrix with 10 energy groups and
      full downscatter.}
    \label{tab:group10dsbj}
  \end{table}
}

@@

      \begin{figure}[t!]
        \begin{center}
          \includegraphics[width=2.25in]{block_jacobi_res.pdf}
        \end{center}
      \end{figure}

@@

    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item Rapidly divergent results
        \medskip
      \item Convergence not achieved with 50 histories per DOF and 90
        minutes compute time
        \medskip
      \item Light water moderator creates a lot of scattering and
        $\mathbf{\rho}(\mathbf{H}) \approx 1$
      \end{itemize}
    \end{column}

@@

      \begin{itemize}
        {\small
        \item Comparison to Trilinos Aztec Krylov solvers with ILUT
          \medskip
        \item MCLS verified for the k-eigenvalue and neutron flux in
          all groups
          \medskip
        \item MCSA converged in fewer iterations than GMRES, more
          iterations than BiCGStab
          \medskip
        \item Explicit preconditioning strategy destroys sparsity and
          elevates CPU times
          \medskip
        \item Spectral radius and memory limitations combine to
          prevent solutions at finer discretizations
        }
      \end{itemize}
